---
title: "`featr` package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

`featr` stands for "feature" (oh, really?) and pronounced the same way.
There is a bunch of functions to produce not-so-common tasks such as 
renaming variables in the data frame or list of data frames,
one-hot-encoding with custom parameters etc. 
Please see [Examples](#examples) section

## Installation

To install `featr` please use `devtools`:

```r
devtools::install_github("pavel-filatov/featr")
```

Please note: you may need to install development version of `rlang` package
**before** the installation of `featr`:
```r
devtools::install_github("r-lib/rlang")
```

## Examples 

#### `cor_index()` 

`cor_index()` fucntion makes a correlation index: it gets each pair of variables, calculate 
correlation between them, and turn it all to data frame. 
Then the function sort data frame by absolute value of correlation.
```{r}
featr::cor_index(mtcars)
```


#### `identity_index()`

For each pair of variables in input data frame `identity_index()` calculates three numbers:

  - number of entries where first and second variables are equal;
  - number of entries where first and second variables aren't equal;
  - all the other cases (i.e. when one of the entries is `NA`)
  
`identitity_index` is computed as ratio $identity\ index = \frac{identical}{identical + non\_identical}$

`.na_include` flag 

```{r}
set.seed(42)
df <- tibble(letter1 = sample(c(letters[1:3], NA, NaN), 100, TRUE),
             letter2 = sample(c(letters[1:3], NA), 100, TRUE),
             letter3 = sample(c(letters[1:3], NA), 100, TRUE),
             num1 = sample(1:4, 100, TRUE),
             num2 = sample(1:4, 100, TRUE),
             num3 = sample(c(1:3, NA), 100, TRUE))

identity_index(df, .na_include = TRUE)
```

